Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-01-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Figure \ref{utility_gain_value} depicts the utility gain value for ten random communities in each of the four runs. The utility gain is the increase of utility the communities gain by cooperating and joining other communities. Comparing the different search rates, we can see by the high $r$ values of $0.20$ and $0.10$, that all 10 samples were able to find and collaborate with communities that gave them the best values. However, for $r=0.7$ in one case and $r=0.5$ in two cases, they were not able to find and form the optimal community. Figure \ref{utility_gain_ratio}, in the same run, illustrates the ratio of utility gain compared to the communities' initial utility values, rather than the abstract gain value.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
\caption{DDM Utility Gain Value}
\label{utility_gain_value}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
\caption{DDM Utility Gain Ratio}
\label{utility_gain_ratio}
\end{figure}

We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount. We call them the \emph{rational} web services. We compare the results with web services which adopted our DDM model. We call them the \emph{trained} web services. Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values. In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them. The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities. Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.

>>>>

Table \ref{table:valueandgain} depicts the average utility gain value of the communities in each of the four runs. The utility gain is the increase of utility the communities gain by cooperating and joining other communities. The utility gain ratio is the ratio of their final utility over initial utility. Comparing the different search rates, we can see increasing $r$ to value of $0.10$ results in significant performance boost, however the higher rates of $r$ are not increasing the chance of finding better collaborative groups for our communities.

\begin{table}[ht]
\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
r=0.05 & 176.1499 & 6.9690 \\
r=0.07 & 174.6541 & 6.9182 \\
r=0.10 & 159.9462 & 6.2834 \\
r=0.20 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:valueandgain} % is used to refer this table in the text
\end{table}

%\begin{figure}%[!t]
%\centering
%\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
%\caption{DDM Utility Gain Value}
%\label{utility_gain_value}
%\end{figure}
%
%\begin{figure}%[!t]
%\centering
%\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
%\caption{DDM Utility Gain Ratio}
%\label{utility_gain_ratio}
%\end{figure}

We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount. We call it the $rational$ method, in the sense that it is just a rational method and is not aiming to be optimal. We chose 10 random web services and compared the results with web services which adopted our DDM model. Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values. In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them. The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities. Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.
